---
title: "termpaperannex"
output: html_document
date: "2023-04-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message = FALSE}
# Load libraries
options(scipen = 999)
library(tidyverse)
library(rnaturalearth) # provides a map of countries of the entire world
library(rworldmap) # for map generation
library(sf)  # for map generation
library(giscoR)
library(readxl) # loading excel files
library(readr)
library(MASS) # for modelling
library(knitr)
library(dplyr)
library(fastDummies)
source("functions.R") # own functions used to fasten coding (see Annex 2)
```

# Data loading and preparation
```{r, loading relevant data}
# restaurants <- read_csv("data/european_restaurants.csv") # original TripAdvisor data 
# gerset <- restaurants %>% filter(country == "Germany") # Subset of OG data for Germany
# write.csv(gerset, "data/gerset.csv") # save data for Germany to reduce computing time
pop <- read_excel("population.xlsx") # population for the country that is assessed (Source: Eurostats)
touristic_df <- read_csv("tourist_nut2.csv") # data on touristic movemet in Europe (Source: Eurostats)
nuts3 <- st_read("NUTS_RG_20M_2021_3035.shp/NUTS_RG_20M_2021_3035.shp") # NUT3 information (Source: Eurostats)
nuts2 <- nuts3 # for NUT2 information
nut3area <- read_csv("reg_area3.csv") # for area information on nut3 (Source: Eurostats)
nuts3 <- nut3area %>% dplyr::select(geo, OBS_VALUE) %>%
  rename(area = OBS_VALUE, NUTS_ID = geo) %>% 
  merge(., nuts3, by = "NUTS_ID")

gerset <- read_csv("gerset.csv") # Data set for Germany as a subset of the TripAdvisor data
```

Based on the data set for Germany that was created as a simple subset of the TripAdvisor set, we create a new data set, including the NUT3 regions of Germany based on the latitude and longitude of each restaurant.
```{r, Nut2 df}
# building data set to work with
ger_allinfo2 = fn_create_nut(gerset, "DE")
working_set <- ger_allinfo2
mean(working_set$restaurants_per_inhab)
```

# Descriptive Statistics I
First, we needed to view the data we are using for the following research:

```{r, Plot1}
Plot1 <- fn_plot_rest(working_set,1000000000)
ggsave("Plot1.png", plot = Plot1, width = 6, height = 4, dpi = 300)
```
```{r}
Plot1
```

# Filtering based on tourism data
After several tries on how to aggregate the data and cutting it into suitable markets, we used Eurostats data on the number of tourists in Germany to identify less touristic regions to ensure to have markets that are less influenced by people that are not included in our population data. 

```{r, tourism data}
touristic_df <- read_csv("tourist_nut2.csv")
toursitic_21 <- touristic_df %>% subset(TIME_PERIOD == 2021) %>% subset(., grepl("^DE", geo)) %>% dplyr::select(geo, OBS_VALUE)
tnew <- toursitic_21[nchar(toursitic_21$geo) == 4, ]
min <- tnew[order(tnew$OBS_VALUE), ][1:20, ]
smallest_values <- subset(tnew, OBS_VALUE %in% min$OBS_VALUE)
tourismfilter <- as.list(unique(smallest_values$geo))
working_set <- ger_allinfo2[grepl(paste(tourismfilter, collapse = "|"), ger_allinfo2$NUTS_ID),]
```

# Set-up for first regression
Based on the now filtered data we started to create our first regression set. The grouping and filtering of the data follows in parts the Lab3 from the lecture (BAN-440 summer term 2023, NHH Bergen Norway)
```{r, first regression set}
working_set$n_rest <- working_set$n_rest %>% as.numeric()
regression_set <- working_set %>% 
  group_by(NUTS_ID) %>% 
  summarise(Population = (mean(Population))/1000, #88% of people in Germany over 20
            MOUNT_TYPE = mean(MOUNT_TYPE),
            URBN_TYPE = mean(URBN_TYPE),
            COAST_TYPE = mean(COAST_TYPE),
            n_rest = mean(n_rest),
            area = mean(area)) %>% 
        subset(area < 700 & Population < 500)
```


# Descriptive Statistics II

```{r, Plot2}
geom <- ger_allinfo2 %>% group_by(NUTS_ID) %>% dplyr::select(geometry) %>% unique()
nut_plot <- ger_allinfo2 %>% group_by(NUTS_ID) %>% summarise(dummy = length(restaurant_link))
plot_set <- working_set %>% merge(., nut_plot, all = TRUE) %>% group_by(NUTS_ID) %>% dplyr::select(restaurants_per_inhab) %>% unique() %>% merge(., geom)
plot_set[is.na(plot_set)] <- 0

Plot2 <- fn_plot_rest(plot_set,1000000000)
ggsave("Plot2.png", plot = Plot2, width = 6, height = 4, dpi = 300)

```
```{r}
Plot2
```

